Combining parsing with sentence understanding

### 2016-03-10 writing/hard_stack_paper/paper.tex
Abstract update.

Tree-structured neural networks are highly as effective sentence models, but they can only operate on parsed sentences, and do not support batched computation, making them prohibitively slow for large-scale tasks. This paper presents the parser-interpreter neural network, which reimplements a tree-structured network within a transition-based neural constituency parser. This allows us to address both weaknesses: the transition-based architecture of the parser makes it possible to perform tree-structured interpretation in an efficient batched setting, and the integrated parser allows the model to interpret unparsed data with nearly no loss in accuracy. In addition, our model supports a novel and effective method for handling local context in sentence interpretation and integrates will with soft attention methods for sentence pair tasks.

>>>>

Tree-structured neural networks integrate valuable syntactic parse information into the process of interpreting sentence meaning, but suffer two key technical problems. They can only operate on parsed sentences and do not directly support batched computation, making them slow and unwieldy for large-scale NLP tasks. We address these issues by introducing the Parser-Interpreter Neural Network (PINN), which simulates tree-structured sentence interpretation within the sequential structure of a transition-based neural parser. This model  supports batched computation, and its integrated parser allows it to operate on unparsed data with nearly no loss of accuracy. We evaluate it on the Stanford NLI entailment task, show that it outperforms other sentence encoding models, and show that it can be integrated effectively with soft attention for sentence pair tasks like entailment for further gains in performance.
